### 2020-08-20 auxilary_scripts/Finrep_data_comparison.Rmd
add import and process functions for oracle finrep data

```{r load_libraries}

library(devtools)

load_all()

library(tidyverse)

```

```{r Import_data}

short_df = import.boi.finrep.data()

long_df = import.boi.oracle.finrep.data()

long_df = long_df %>%
  filter(report_period == "quarterly")

```

```{r gazit_glob_comparison}

X = full_join(
  long_df %>% 
    filter(tase_id == 126) %>% 
    filter(year(date_yearmon) %in% c(2000,2007,2010)) %>% 
    mutate(date_yearqtr = as.yearqtr(date_yearmon)) %>% 
    mutate(total_assets = as.numeric(total_assets) / 1000) %>% 
    select(tase_id, date_yearmon,date_yearqtr, total_assets),
  short_df %>% 
  filter(TASE_ID == 126) %>% 
  filter(year(Date) %in% c(2000,2007,2010)) %>% 
  mutate(Total_Assets = as.numeric(Total_Assets)) %>% 
  select(TASE_ID,Date, Total_Assets),
  by = c("total_assets" = "Total_Assets")
  ) %>% 
  select(date_yearmon,date_yearqtr,Date,total_assets)

X %>% 
  mutate(Month = month(date_yearmon)) %>% 
  arrange(Date) %>% 
  select(Month, everything())

```

### 2020-08-20 R/Import_functions.R

@@ -15,19 +15,38 @@ import.boi.finrep.data = function(filepath = NULL){
     "\\OneDrive - Bank Of Israel\\Data\\",
     "TASE liquidity\\FinancialReports.csv")}
 
-  temp_df = read.csv(filepath, encoding = "UTF-8", header = FALSE,
+  temp_df = read.csv(filepath, encoding = "UTF-8",
+                     header = FALSE,
                      stringsAsFactors = FALSE)
 
-  names_vec = c("Year","Date","TASE_branch","TASE_ID","Entity_Name",
-                "Entity_ID","Total_Assets","Current_Assets",
-                "Cash_Equivalent","Non_Current_Assets",
-                "Total_Liabilities","Current_Liabilities",
-                "Non_current_Liabilities","Equity","Minority_rights",
-                "Revenue","Total_Cost","Operating_Profit",
-                "Financing_cost","Profit_before_tax",
-                "Tax","Net_Profit","Minority_Profit",
-                "Operating_CashFlow",
-                "Capex_CashFlow","Financial_CashFlow")
+  names_vec = c(
+    "Year",
+    "Date",
+    "TASE_branch",
+    "TASE_ID",
+    "Entity_Name",
+    "Entity_ID",
+    "Total_Assets",
+    "Current_Assets",
+    "Cash_Equivalent",
+    "Non_Current_Assets",
+    "Total_Liabilities",
+    "Current_Liabilities",
+    "Non_current_Liabilities",
+    "Equity",
+    "Minority_rights",
+    "Revenue",
+    "Total_Cost",
+    "Operating_Profit",
+    "Financing_cost",
+    "Profit_before_tax",
+    "Tax",
+    "Net_Profit",
+    "Minority_Profit",
+    "Operating_CashFlow",
+    "Capex_CashFlow",
+    "Financial_CashFlow"
+  )
 
   df = temp_df %>%
     slice(-1) %>%
@@ -37,15 +56,17 @@ import.boi.finrep.data = function(filepath = NULL){
 
   Sys.setlocale(locale = "hebrew")
 
-  levels(df$TASE_branch) = list("Biomed" = "ביומד",
-                                "Insurance" = "ביטוח",
-                                "Banks" = "בנקים",
-                                "Investment_Holdings" = "השקעה ואחזקות",
-                                "Technology" = "טכנולוגיה",
-                                "Services" = "מסחר ושרותים",
[…]

### 2020-08-20 R/Process_functions.R

@@ -19,12 +19,90 @@ make_finrep_df = function(raw_df, selected_x_vars = NULL,
 
   finrep_df = finrep_df %>%
     select(-starts_with("entity")) %>%
-    mutate(across(-c(starts_with("tase"),"year") & where(is.character),
+    mutate(across(-c(starts_with("tase"),"year") &
+                    where(is.character),
                   as.numeric)) %>%
     mutate(leverage = total_liabilities / total_assets) %>%
     mutate(capex_to_revenue = capex_cashflow / revenue) %>%
     mutate(roa = operating_profit / total_assets) %>%
     mutate(free_cashflow = operating_cashflow / total_assets)
+
+
+  if(!is.null(selected_x_vars)){
+
+    finrep_df = finrep_df %>%
+      select(date, tase_id, any_of(selected_x_vars))
+
+  }
+
+
+
+  if(filter_df){
+
+    finrep_df = finrep_df %>%
+      filter(complete.cases(.)) %>%
+      filter(across(where(is.numeric), is.finite))
+
+  }
+
+
+  return(finrep_df)
+
+
+
+
+
+
+}
+
+
+#' @title Prepare financial reports data
+#'
+#' @details This function prepares the financial reports
+#' variables data from Oracle format
+#'
+#' @import dplyr
+#'
+make_finrep_oracle_df = function(raw_oracle_df,
+                          selected_x_vars = NULL,
+                          filter_df = FALSE){
+
+  x_vars = c(
+    "leverage",
+    "capex_to_revenue",
+    "roa",
+    "free_cashflow",
+    "intangible",
+    ""
+  )
+
+
+
+  finrep_df = raw_oracle_df %>%
+    filter(report_period == "quarterly")
+
+
+  finrep_df = finrep_df %>%
+    select(-c("fsd_period",
+              "report_period",
+              "be_master_gk",
+              "be_ver_gk",
+              "date_fsd",
+              "company_id",
+              "business_entity_name",
+              "firm_merchantability_heb"
+              ))
+
+  finrep_df = finrep_df %>%
+    mutate(across(c(-date_yearqtr,-starts_with("is")),
+                  as.numeric))
+
+  finrep_df = finrep_df %>%
+    mutate(leverage = total_liabilities / total_assets) %>%
+    mutate(capex_to_revenue =
+             investing_activities / total_revenue) %>%
+    mutate(roa = operating_profit / total_assets) %>%
[…]

### 2020-08-21 R/Process_functions.R
bugfixes in oracle finrep import

@@ -59,7 +59,8 @@ make_finrep_df = function(raw_df, selected_x_vars = NULL,
 #' @title Prepare financial reports data
 #'
 #' @details This function prepares the financial reports
-#' variables data from Oracle format
+#' variables data from Oracle format. The original values are given in thousands ILS
+#' and are scaled down by 1000 so that the result is in millions ILS
 #'
 #' @import dplyr
 #'
@@ -79,12 +80,12 @@ make_finrep_oracle_df = function(raw_oracle_df,
 
 
   finrep_df = raw_oracle_df %>%
-    filter(report_period == "quarterly")
+    filter(reporting_period == "quarterly")
 
 
   finrep_df = finrep_df %>%
     select(-c("fsd_period",
-              "report_period",
+              "reporting_period",
               "be_master_gk",
               "be_ver_gk",
               "date_fsd",
@@ -94,8 +95,11 @@ make_finrep_oracle_df = function(raw_oracle_df,
               ))
 
   finrep_df = finrep_df %>%
-    mutate(across(c(-date_yearqtr,-starts_with("is")),
+    mutate(across(c(-date_yearqtr,-starts_with("is"), -tase_id),
                   as.numeric))
+
+  finrep_df = finrep_df %>%
+    mutate(across(where(is.numeric), ~ . * 10 ^ (-3)))
 
   finrep_df = finrep_df %>%
     mutate(leverage = total_liabilities / total_assets) %>%
@@ -186,14 +190,14 @@ make_market_df = function(df){
 #'
 #' @param raw_data list of finrep and market data
 #'
-#' @
+#'
 make_reg_df = function(market_df, finrep_df, secs_catalog){
 
   merged_df = market_df %>%
     left_join(secs_catalog %>%
                 select(sec_id, tase_id) %>%
                 distinct(), by = "sec_id") %>%
-    inner_join(finrep_df, by = c("tase_id","date_yearqtr" = "date"))
+    inner_join(finrep_df, by = c("tase_id","date_yearqtr"))
 
 
   df = merged_df %>%

### 2020-08-21 auxilary_scripts/Finrep_data_comparison.Rmd
add oracle and nimrod comparison

@@
+----
+title: Financial reports data  - comparison of sources
+----
+
+The main conclusion is that there are differences between Oracle, Mos and Nimrod's data. However the differences are not systematic, for the same tase_id, variable and
+date there are sometimes identical observations and sometimes a diffrerent ones.
+
 ```{r load_libraries}
@@
 
-short_df = import.boi.finrep.data()
+secs_catalog = read_csv(paste0(
+  "C:\\Users\\internet\\OneDrive - Bank Of Israel",
+  "\\Data\\TASE liquidity\\Secs_Catalog.csv")) %>% 
+  mutate(across(c("tase_id","sec_id"), as.character))
 
-long_df = import.boi.oracle.finrep.data()
+mos_df = import.boi.finrep.data() %>% 
+  rename_all(tolower) %>% 
+  rename(date_yearqtr = date) %>% 
+  rename(total_net_profit = net_profit)
 
-long_df = long_df %>%
-  filter(report_period == "quarterly")
+oracle_df  = import.boi.oracle.finrep.data() %>%
+  filter(reporting_period == "quarterly")
+
+nimrod_df = import.nimrod.stata.df(paste0(
+  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
+  "\\OneDrive - Bank Of Israel\\Data\\",
+  "TASE liquidity\\Stata files",
+  "\\TASE panel.dta")
+  ) %>% 
+  rename(date_yearqtr = date)
 
@@
 
-```{r gazit_glob_comparison}
+\section{Oracle vs Mos comparison}
 
-X = full_join(
-  long_df %>% 
-    filter(tase_id == 126) %>% 
-    filter(year(date_yearmon) %in% c(2000,2007,2010)) %>% 
-    mutate(date_yearqtr = as.yearqtr(date_yearmon)) %>% 
-    mutate(total_assets = as.numeric(total_assets) / 1000) %>% 
-    select(tase_id, date_yearmon,date_yearqtr, total_assets),
-  short_df %>% 
-  filter(TASE_ID == 126) %>% 
-  filter(year(Date) %in% c(2000,2007,2010)) %>% 
-  mutate(Total_Assets = as.numeric(Total_Assets)) %>% 
-  select(TASE_ID,Date, Total_Assets),
-  by = c("total_assets" = "Total_Assets")
-  ) %>% 
-  select(date_yearmon,date_yearqtr,Date,total_assets)
+```{r oracle_mos_df}
 
-X %>% 
-  mutate(Month = month(date_yearmon)) %>% 
-  arrange(Date) %>% 
-  select(Month, everything())
+oracle_mos_diff_df = full_join(
+  oracle_df %>% 
+    select(intersect(names(.), names(mos_df))) %>% 
+    mutate(across(-c("tase_id", "date_yearqtr"), ~ as.numeric(.) * 10 ^ (-3))) %>% 
+    pivot_longer(-c("tase_id", "date_yearqtr"),
+                 names_to = "feature", values_to = "oracle"),
+  mos_df %>% 
+    select(intersect(names(.), names(oracle_df))) %>% 
+    mutate(across(-c("tase_id", "date_yearqtr"),as.numeric)) %>%  
+    pivot_longer(-c("tase_id", "date_yearqtr"),
+                 names_to = "feature", values_to = "mos"),
+  by = c("tase_id","date_yearqtr","feature"))%>% 
+  rowwise() %>% 
+  mutate(diff = abs((oracle - mos) / mean(c(oracle,mos))) * 100) %>% 
+  ungroup() %>% 
+  arrange(desc(diff))
 
 ```
+
+There are some differences between oracle and mos databases.
+In the case of Aura company oracle database is correct
+(for example the comparison of 2019Q1 profit). For Brand company mos is correct.
+
+\section{Oracle vs Nimrod comparison}
+
+```{r oracle_nimrod_df}
+
+oracle_nimrod_diff_df = full_join(
+  oracle_df %>% 
+    select(intersect(names(.), names(nimrod_df))) %>% 
+    mutate(across(-c("tase_id", "date_yearqtr"), ~ as.numeric(.) * 10 ^ (-3))) %>% 
+    pivot_longer(-c("tase_id", "date_yearqtr"),
+                 names_to = "feature", values_to = "oracle"),
+  nimrod_df %>% 
+    select(intersect(names(.), names(oracle_df))) %>% 
+    mutate(across(-c("tase_id", "date_yearqtr"), ~ as.numeric(.) * 10 ^ (-3))) %>% 
+    mutate(across(-c("tase_id", "date_yearqtr"),as.numeric)) %>%  
+    pivot_longer(-c("tase_id", "date_yearqtr"),
+                 names_to = "feature", values_to = "nimrod"),
+  by = c("tase_id","date_yearqtr","feature"))%>% 
+  rowwise() %>% 
+  mutate(diff = abs((oracle - nimrod) / mean(c(oracle,nimrod))) * 100) %>% 
+  ungroup() %>% 
+  arrange(desc(diff))
+
+discrep_df = oracle_nimrod_diff_df %>% 
+  filter(diff > 5) %>% 
+  left_join(secs_catalog[,c("tase_id","comp_name_heb")])
+
+```
+
+There are

### 2020-08-21 auxilary_scripts/Finrep_data_comparison.Rmd
move comparison to separate script

@@
-----
+---
 title: Financial reports data  - comparison of sources
-----
+---
+
+```{r import_temp_data}
+
+raw_data = read_rds(paste0(
+  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
+  "\\OneDrive - Bank Of Israel\\Data\\TASE",
+  " liquidity\\Current cache files\\raw_data.RDS"))
+
+vars_status = read_csv(paste0(
+  file.path(Sys.getenv("USERPROFILE"),fsep="\\"),
+  "\\OneDrive - Bank Of Israel\\Data\\TASE",
+  " liquidity\\Variables_List.csv"))
+
+```
+
+\subsection{Financial reports}
+
+This dataset has data on financial reports of TASE companies.
+The data covers `r length(unique(raw_data$finrep_df$tase_id))` companies for the period `r paste0(range(raw_data$finrep_df$date), collapse = "-")` at quarterly frequency.
+
+```{r summary_finrep_df, results='asis', eval=FALSE}
+
+stargazer(raw_data$finrep_df %>% 
+            select(-date_yearqtr,-tase_id) %>% 
+            as.data.frame(),
+          summary = TRUE, header = FALSE, digits = 2,
+          summary.stat = c("n","mean","median","max","min"))
+
+```
+
+\subsection{Market data}
+A dataset with market data (market capitalization, turnover) that allows to calculate Amihud's iiliquidity measure.
+The data time period is `r paste0(range(raw_data$market_df$date_yearqtr), collapse = "-")` at quarterly frequency.
+
+```{r summary_market_df, results='asis', eval=FALSE}
+
+stargazer(raw_data$market_df %>% 
+            select(-sec_id,-date_yearqtr) %>% 
+            as.data.frame(),
+          summary = TRUE, header = FALSE, digits = 2)
+
+```
+
+\subsection{Nimrod's dataset}
+
+```{r Import_nimrod_dataset}
+
+raw_data$nimrod_stata_df = import.nimrod.stata.df(paste0(
+  file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
+  "\\OneDrive - Bank Of Israel\\Data\\",
+  "TASE liquidity\\Stata files",
+  "\\TASE panel.dta")
+  )
+
+stata_df = raw_data$nimrod_stata_df %>% 
+  select(any_of(parameters_list$nimrod_vars))
+
+```
+
+A dataset that was gathered by Nimrod . The data covers `r length(unique(stata_df$tase_id))` companies for the period `r paste0(range(stata_df$date), collapse = "-")` at quarterly frequency. 
+The data adresses several categories:
+
+\begin{itemize}
+  \item
+  Financial Reports
+  \item
+  Market data
+\end{itemize}
+
+```{r summary_df_stata, results="asis", eval=FALSE}
+
+stargazer(stata_df %>% 
+            select(-starts_with("tase"),-date) %>% 
+            as.data.frame(),
+          summary = TRUE,
+          header = FALSE,
+          summary.stat = c("n","mean","median","max","min"))
+
+```
+
+```{r plot_NA, eval=FALSE}
+
+stata_df %>% 
+  slice_sample(n = 1000) %>% 
+  group_by(date) %>% 
+  mutate(across(everything(), ~is.na(.))) %>% 
+  pivot_longer(-date) %>% 
+  ggplot(aes(x = date, y = name, color = value)) + 
+  scale_color_manual(values = c("TRUE" = "magenta", "FALSE" = "gray")) + 
+  geom_point(show.legend = FALSE) + 
+  theme_bw()
+
+```
+
+\subsubsection{Comparison of financial reports data}
 
@@
 There are
+
+```{r diff_example}
+
+inner_join(oracle_mos_diff_df %>% 
+  filter(tase_id == 666) %>% 
+  select(-diff),
+  oracle_nimrod_diff_df %>% 
+  filter(tase_id == 666) %>% 
+  select(-diff)) %>% 
+  filter(feature == "operating_profit") %>% 
+  pivot_longer(oracle:nimrod,names_to = "source") %>% 
+  ggplot(aes(x = date_yearqtr, y = value, color = source)) + 
+  geom_line() + 
+  xlab(NULL) + ylab(NULL) + ggtitle("Amos Luzon group operating profit") + 
+  theme_bw() + 
+  theme(legend.position = "bottom")
+
+```

### 2022-10-02 R/Import_functions.R
update wfe data

@@ -130,13 +130,13 @@ import.boi.market.data = function(filepath = NULL){
 #'
 #' @import xts
 
-import.TASE.comps_status = function(filepath = NULL){
+import_TASE_comps_status = function(filepath = NULL){
 
-  if(is.null(filepath)){filepath = paste0(
-    file.path(Sys.getenv("USERPROFILE"),"Documents",
-              fsep="\\"),
-    "\\Data\\TASE\\TASE_Liquidity\\",
-    "Trading_Companies_Status.xlsx")}
+  if(is.null(filepath)){
+    filepath = paste0(Sys.getenv("USERPROFILE"),
+                      "\\OneDrive - Bank Of Israel",
+                      "\\Data\\TASE liquidity",
+                      "\\Trading_Companies_Status.xlsx")}
 
   sheets_names = excel_sheets(filepath)
 

### 2022-10-03 R/Import_functions.R
update TASE_comps_desc

@@ -143,14 +143,20 @@ import_TASE_comps_status = function(filepath = NULL){
   sheet_list = lapply(sheets_names,function(temp_name){
 
     temp_sheet = read_xlsx(filepath,sheet = temp_name) %>%
-      mutate(Year = temp_name) %>%
-      rename(Start_Year = Start, End_Year = End, Issued_Comps = Issued,
-             Delisted_Comps = Delisted) %>%
-      select(Year, Sector, everything())
+      mutate(year = temp_name) %>%
+      rename_all(tolower) %>%
+      rename(start_year = start, end_year = end,
+             issued_comps = issued,
+             delisted_comps = delisted) %>%
+      select(year, sector, everything())
 
   })
 
   status_df = bind_rows(sheet_list)
+
+  status_df = status_df %>%
+    mutate(across(where(is.numeric), ~replace_na(.,0)))
+
 
   return(status_df)
 

### 2022-11-15 R/Auxilary_functions.R
import bew data and update functions

@@ -8,7 +8,7 @@
 #'
 #' @param market_df a data frame with price and turnover data at daily frequency
 
-calculate.iiliq = function(market_df){
+calculate_illiq = function(market_df){
 
   market_df = market_df %>%
     arrange(date)

### 2022-11-15 R/Import_functions.R

@@ -89,7 +89,7 @@ import.boi.finrep.data = function(filepath = NULL){
 #' @export
 
 
-import.boi.market.data = function(filepath = NULL){
+import_boi_market_data = function(filepath = NULL){
 
   if(is.null(filepath)){filepath = paste0(file.path(
     Sys.getenv("USERPROFILE"),fsep="\\"),
@@ -105,7 +105,7 @@ import.boi.market.data = function(filepath = NULL){
            sec_id = security_ident_num_tase,
            close = close_rate_adj,
            date = date_value) %>%
-    mutate(date = ymd(ymd_hms(date))) %>%
+    mutate(date = as_date(date)) %>%
     mutate(sec_id = as.character(as.numeric(sec_id)))
 
 
@@ -129,6 +129,8 @@ import.boi.market.data = function(filepath = NULL){
 #' @import dplyr
 #'
 #' @import xts
+#'
+#' @export
 
 import_TASE_comps_status = function(filepath = NULL){
 

### 2022-11-15 R/Process_functions.R

@@ -10,8 +10,7 @@ make_finrep_df = function(raw_df, selected_x_vars = NULL,
     "capex_to_revenue",
     "roa",
     "free_cashflow",
-    "intangible",
-    ""
+    "intangible"
   )
 
   finrep_df = raw_df %>%
@@ -146,7 +145,7 @@ make_finrep_oracle_df = function(raw_oracle_df,
 make_market_df = function(df){
 
   illiq_df = df %>%
-    calculate.iiliq() %>%
+    calculate_illiq() %>%
     group_by(sec_id, date_yearqtr = as.yearqtr(date_yearmon)) %>%
     summarise(illiq = mean(illiq, na.rm = TRUE), .groups = "drop")
 
@@ -154,10 +153,7 @@ make_market_df = function(df){
     select(date,sec_id, close) %>%
     group_by(sec_id) %>%
     arrange(date) %>%
-    mutate(ret = slide_dbl(close,
-                           .f = ~.[2] / .[1] - 1,
-                           .before = 1,
-                           .complete = TRUE)) %>%
+    mutate(ret = c(NA,diff(log(close)))) %>%
     group_by(sec_id, date_yearqtr = as.yearqtr(date)) %>%
     summarise(volatility = sd(ret, na.rm = TRUE), .groups = "drop")
 
@@ -169,9 +165,7 @@ make_market_df = function(df){
     mutate(size = log(market_value)) %>%
     group_by(sec_id, date_yearqtr = as.yearqtr(date)) %>%
     summarise(across(c(size, market_value, turnover, volume),
-                     mean, na.rm = TRUE), .groups = "drop")%>%
-    filter_at(.vars = vars(size,market_value,turnover, volume),
-              any_vars(!is.na(.)))
+                     mean, na.rm = TRUE), .groups = "drop")
 
  market_df = market_df %>%
    full_join(illiq_df, by = c("sec_id","date_yearqtr")) %>%

### 2022-11-16 R/Process_functions.R
update dataset comparison with nimrod data and workdraft

@@ -72,26 +72,22 @@ make_finrep_oracle_df = function(raw_oracle_df,
     "capex_to_revenue",
     "roa",
     "free_cashflow",
-    "intangible",
-    ""
-  )
-
-
-
-  finrep_df = raw_oracle_df %>%
-    filter(reporting_period == "quarterly")
+    "intangible_assets")
 
 
   finrep_df = finrep_df %>%
-    select(-c("fsd_period",
-              "reporting_period",
-              "be_master_gk",
-              "be_ver_gk",
-              "date_fsd",
-              "company_id",
-              "business_entity_name",
-              "firm_merchantability_heb"
-              ))
+    select(-any_of(
+      c(
+        "fsd_period",
+        "reporting_period",
+        "be_master_gk",
+        "be_ver_gk",
+        "date_fsd",
+        "company_id",
+        "business_entity_name",
+        "firm_merchantability_heb"
+      )
+    ))
 
   finrep_df = finrep_df %>%
     mutate(across(c(-date_yearqtr,-starts_with("is"), -tase_id),
@@ -111,7 +107,7 @@ make_finrep_oracle_df = function(raw_oracle_df,
   if(!is.null(selected_x_vars)){
 
     finrep_df = finrep_df %>%
-      select(date, tase_id, any_of(selected_x_vars))
+      select(date = date_yearqtr, tase_id, any_of(selected_x_vars))
 
   }
 
@@ -146,7 +142,7 @@ make_market_df = function(df){
 
   illiq_df = df %>%
     calculate_illiq() %>%
-    group_by(sec_id, date_yearqtr = as.yearqtr(date_yearmon)) %>%
+    group_by(sec_id, date = as.yearqtr(date_yearmon)) %>%
     summarise(illiq = mean(illiq, na.rm = TRUE), .groups = "drop")
 
   sd_df = df %>%
@@ -154,7 +150,7 @@ make_market_df = function(df){
     group_by(sec_id) %>%
     arrange(date) %>%
     mutate(ret = c(NA,diff(log(close)))) %>%
-    group_by(sec_id, date_yearqtr = as.yearqtr(date)) %>%
+    group_by(sec_id, date = as.yearqtr(date)) %>%
     summarise(volatility = sd(ret, na.rm = TRUE), .groups = "drop")
 
 
@@ -163,13 +159,13 @@ make_market_df = function(df){
     mutate(across(c(market_value, turnover),
[…]

### 2022-11-19 R/Import_functions.R
update to Oracle data 15_11_2022 and rewrite dataset description

@@ -89,12 +89,8 @@ import.boi.finrep.data = function(filepath = NULL){
 #' @export
 
 
-import_boi_market_data = function(filepath = NULL){
+import_boi_market_data = function(filepath){
 
-  if(is.null(filepath)){filepath = paste0(file.path(
-    Sys.getenv("USERPROFILE"),fsep="\\"),
-    "\\OneDrive - Bank Of Israel\\Data\\",
-    "TASE liquidity\\Rdata files\\stocks_full_data.rds")}
 
   temp_df = read_rds(filepath)
 
@@ -233,7 +229,7 @@ import.nimrod.stata.df = function(filepath,
   names_table = read_csv(paste0(
     file.path(Sys.getenv("USERPROFILE"),fsep = "\\"),
     "\\OneDrive - Bank Of Israel\\Data\\",
-    "TASE liquidity\\convert_names_table.csv")) %>%
+    "TASE liquidity\\michael files\\convert_names_table.csv")) %>%
     filter(old_name %in% names(raw_df))
 
   df = raw_df %>%
@@ -262,7 +258,7 @@ import.nimrod.stata.df = function(filepath,
 }
 
 
-#' @title Import Orcale format financial report data
+#' @title Import Oracle format financial report data
 #'
 #' @description  This function imports financial report data from Oracle format
 #'

### 2022-11-19 R/Process_functions.R

@@ -64,34 +64,15 @@ make_finrep_df = function(raw_df, selected_x_vars = NULL,
 #' @import dplyr
 #'
 make_finrep_oracle_df = function(raw_oracle_df,
-                          selected_x_vars = NULL,
-                          filter_df = FALSE){
+                                 raw_finrep_vars,
+                                 final_finrep_vars){
 
-  x_vars = c(
-    "leverage",
-    "capex_to_revenue",
-    "roa",
-    "free_cashflow",
-    "intangible_assets")
 
+  finrep_df = raw_oracle_df %>%
+    select(tase_id, date = date_yearqtr, any_of(raw_finrep_vars))
 
   finrep_df = finrep_df %>%
-    select(-any_of(
-      c(
-        "fsd_period",
-        "reporting_period",
-        "be_master_gk",
-        "be_ver_gk",
-        "date_fsd",
-        "company_id",
-        "business_entity_name",
-        "firm_merchantability_heb"
-      )
-    ))
-
-  finrep_df = finrep_df %>%
-    mutate(across(c(-date_yearqtr,-starts_with("is"), -tase_id),
-                  as.numeric))
+    mutate(across(-c("tase_id", "date"),as.numeric))
 
   finrep_df = finrep_df %>%
     mutate(across(where(is.numeric), ~ . * 10 ^ (-3)))
@@ -103,23 +84,9 @@ make_finrep_oracle_df = function(raw_oracle_df,
     mutate(roa = operating_profit / total_assets) %>%
     mutate(free_cashflow = operating_activities / total_assets)
 
+  finrep_df = finrep_df %>%
+    select(tase_id, date, any_of(final_finrep_vars))
 
-  if(!is.null(selected_x_vars)){
-
-    finrep_df = finrep_df %>%
-      select(date = date_yearqtr, tase_id, any_of(selected_x_vars))
-
-  }
-
-
-
-  if(filter_df){
-
-    finrep_df = finrep_df %>%
-      filter(complete.cases(.)) %>%
-      filter(across(where(is.numeric), is.finite))
-
-  }
 
 
   return(finrep_df)
@@ -140,32 +107,31 @@ make_finrep_oracle_df = function(raw_oracle_df,
 #'
 make_market_df = function(df){
 
-  illiq_df = df %>%
-    calculate_illiq() %>%
-    group_by(sec_id, date = as.yearqtr(date_yearmon)) %>%
[…]

### 2022-11-20 R/Import_functions.R
update matching to match on market cap and assets

@@ -128,46 +128,6 @@ import_boi_market_data = function(filepath){
 #'
 #' @export
 
-import_TASE_comps_status = function(filepath = NULL){
-
-  if(is.null(filepath)){
-    filepath = paste0(Sys.getenv("USERPROFILE"),
-                      "\\OneDrive - Bank Of Israel",
-                      "\\Data\\TASE liquidity",
-                      "\\Trading_Companies_Status.xlsx")}
-
-  sheets_names = excel_sheets(filepath)
-
-  sheet_list = lapply(sheets_names,function(temp_name){
-
-    temp_sheet = read_xlsx(filepath,sheet = temp_name) %>%
-      mutate(year = temp_name) %>%
-      rename_all(tolower) %>%
-      rename(start_year = start, end_year = end,
-             issued_comps = issued,
-             delisted_comps = delisted) %>%
-      select(year, sector, everything())
-
-  })
-
-  status_df = bind_rows(sheet_list)
-
-  status_df = status_df %>%
-    mutate(across(where(is.numeric), ~replace_na(.,0)))
-
-
-  return(status_df)
-
-}
-
-
-#' @title Import BoI format financial report data
-#'
-#' @description  This function imports financial report data from BOI format
-#'
-#' @param filepath the path to financial report data (in csv format)
-#'
-#' @import dplyr
 
 import.old.regression.data = function(filepath = NULL){
 
@@ -257,57 +217,4 @@ import.nimrod.stata.df = function(filepath,
 
 }
 
-
-#' @title Import Oracle format financial report data
-#'
-#' @description  This function imports financial report data from Oracle format
-#'
-#' @param filepath the path to financial report data (in csv format)
-#'
-#' @import dplyr
-#'
-#' @import zoo
-#'
-#' @import stringr
-#'
-#' @export
-
-import.boi.oracle.finrep.data = function(filepath = NULL,
-                                         data_frequency){
-
-  if(missing(data_frequency)){stop("data frequency argument is required")}
-
-
-  if(is.null(filepath)){filepath = paste0(file.path(
-    Sys.getenv("USERPROFILE"),fsep="\\"),
-    "\\OneDrive - Bank Of Israel\\Data\\",
-    "TASE liquidity\\Rdata files\\finrep_oracle_data.rds")}
-
-  temp_df = read_rds(filepath)
-
-  df = temp_df %>%
-    rename_all(tolower) %>%
-    rename_all(~str_replace_all(.,"__","_"))
-
[…]

### 2022-11-22 R/Process_functions.R
add function for matching

@@ -176,3 +176,53 @@ make_reg_df = function(market_df, finrep_df,
 
 
 }
+
+
+
+#' This function matches delisted and control companies by
+#' selected varible
+#'
+#'
+match_control_group = function(ipo_comps, data_df,
+                               matching_variable,
+                               threshold){
+
+  data_df = data_df %>%
+    select(tase_id, date, all_of(matching_variable)) %>%
+    filter(complete.cases(.))
+
+  delisted_comps= ipo_comps %>%
+    filter(delisted == 1) %>%
+    select(-delisted) %>%
+    mutate(tase_id = as.character(tase_id)) %>%
+    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
+    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
+    filter(complete.cases(.))
+
+
+  control_comps = ipo_comps %>%
+    filter(delisted == 0) %>%
+    select(-delisted) %>%
+    mutate(tase_id = as.character(tase_id)) %>%
+    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
+    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
+    filter(complete.cases(.))
+
+  del_var = paste0(matching_variable,"_delisted")
+
+  control_var = paste0(matching_variable,"_control")
+
+
+  matching_table = delisted_comps %>%
+    full_join(control_comps,
+              by = "ipo_date",
+              suffix = c("_delisted","_control")) %>%
+    mutate(diff = !!sym(del_var) / !!sym(control_var) - 1) %>%
+    filter(abs(diff) <= threshold) %>%
+    select(starts_with("tase_id"),ipo_date)
+
+  return(matching_table)
+
+
+}
+

### 2022-11-23 R/Auxilary_functions.R
match by size and summarise matching

@@ -49,3 +49,39 @@ calculate.beta.and.car = function(df){
 
 
 }
+
+
+
+#' This function pivots delisted and control comps into
+#' tase_id, date, comp_type format
+#'
+#' @param match_table a data frame with tase_id_delisted,
+#' tase_id_control, ipo_date, delisting_date structure
+#'
+pivot_to_join_format = function(match_table){
+
+  join_format = match_table %>%
+    mutate(time_period = map2(ipo_date, delisting_date,
+                              function(start,end){
+
+                                period = seq.Date(from = start,
+                                                  to = end,
+                                                  by = "quarter") %>%
+                                  as.yearqtr()
+
+                                return(period)
+
+
+                              })) %>%
+    select(starts_with("tase_id"), time_period) %>%
+    pivot_longer(starts_with("tase_id"),
+                 names_to = "comp_type", values_to = "tase_id") %>%
+    mutate(comp_type = str_remove_all(comp_type,"tase_id_")) %>%
+    distinct() %>%
+    unnest(time_period)
+
+
+  return(join_format)
+
+
+}

### 2022-11-23 R/Import_functions.R

@@ -217,4 +217,42 @@ import.nimrod.stata.df = function(filepath,
 
 }
 
+#' This function imports comps data that includes tase_id,
+#' ipo_date, delisting_date and quotation_period
+#'
+#' @param ipo_dates_filepath
+#' @param delisting_dates_filepath
 
+import_comps_dates_and_status = function(ipo_dates_filepath,
+                             delisting_dates_filepath){
+
+  ipo_dates = read_csv(ipo_dates_filepath,
+                       show_col_types = FALSE) %>%
+    select(tase_id, ipo_date) %>%
+    mutate(ipo_date = dmy(ipo_date)) %>%
+    arrange(tase_id)
+
+
+  delisted_dates = read_csv(delisting_dates_filepath,
+                            show_col_types = FALSE) %>%
+    arrange(tase_id) %>%
+    mutate(delisting_date = mdy(delisting_date))
+
+
+  comps_data = ipo_dates %>%
+    full_join(delisted_dates, by = "tase_id") %>%
+    mutate(quotation_period = difftime(delisting_date, ipo_date)) %>%
+    mutate(quotation_period = time_length(quotation_period,"years"))  %>%
+    mutate(across(starts_with("tase_id"), as.character)) %>%
+    filter(quotation_period >= 0 | is.na(quotation_period)) %>%
+    group_by(tase_id, ipo_date) %>%
+    arrange(ipo_date, delisting_date) %>%
+    slice(1) %>%
+    ungroup() %>%
+    filter(year(ipo_date) >= 2005)
+
+  return(comps_data)
+
+
+
+}

### 2022-11-23 R/Process_functions.R

@@ -182,8 +182,15 @@ make_reg_df = function(market_df, finrep_df,
 #' This function matches delisted and control companies by
 #' selected varible
 #'
+#' @param comps_list table with tase_ id, ipo_date, delisted_status
 #'
-match_control_group = function(ipo_comps, data_df,
+#' @param matching_variable the variable control group is matched on
+#'
+#' @param threshold allowed percentage difference between delisted
+#'  and control comps
+#'
+#'
+match_control_group = function(comps_list, data_df,
                                matching_variable,
                                threshold){
 
@@ -191,18 +198,18 @@ match_control_group = function(ipo_comps, data_df,
     select(tase_id, date, all_of(matching_variable)) %>%
     filter(complete.cases(.))
 
-  delisted_comps= ipo_comps %>%
-    filter(delisted == 1) %>%
-    select(-delisted) %>%
+  delisted_comps= comps_list %>%
+    filter(delisted_status == 1) %>%
+    select(tase_id, ipo_date) %>%
     mutate(tase_id = as.character(tase_id)) %>%
     mutate(ipo_date = as.yearqtr(ipo_date)) %>%
     left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
     filter(complete.cases(.))
 
 
-  control_comps = ipo_comps %>%
-    filter(delisted == 0) %>%
-    select(-delisted) %>%
+  control_comps = comps_list %>%
+    filter(delisted_status == 0) %>%
+    select(tase_id, ipo_date) %>%
     mutate(tase_id = as.character(tase_id)) %>%
     mutate(ipo_date = as.yearqtr(ipo_date)) %>%
     left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
@@ -219,7 +226,8 @@ match_control_group = function(ipo_comps, data_df,
               suffix = c("_delisted","_control")) %>%
     mutate(diff = !!sym(del_var) / !!sym(control_var) - 1) %>%
     filter(abs(diff) <= threshold) %>%
-    select(starts_with("tase_id"),ipo_date)
+    select("tase_id_delisted","tase_id_control") %>%
+    mutate(across(starts_with("tase_id"),as.character))
 
   return(matching_table)
 

### 2022-11-23 R/Process_functions.R
add univriate comparison of control vs delisted comps

@@ -234,3 +234,37 @@ match_control_group = function(comps_list, data_df,
 
 }
 
+#' This function returns matched df
+#'
+#'
+get_matched_df = function(df, comps_dates,
+                          matching_variable,
+                          threshold){
+
+
+  matched_table = comps_dates %>%
+    mutate(delisted_status = if_else(is.na(quotation_period),0,1)) %>%
+    select(tase_id, ipo_date, delisted_status) %>%
+    match_control_group(data_df = df,
+                        matching_variable = matching_variable,
+                        threshold = threshold)
+
+
+  matched_comps_df = matched_table %>%
+    left_join(comps_dates %>%
+                select(tase_id, contains("date")),
+              by = c("tase_id_delisted" = "tase_id")) %>%
+    pivot_to_join_format() %>%
+    left_join(df, by = c("tase_id",c("time_period" = "date")))
+
+  return(matched_comps_df)
+
+
+
+
+}
+
+
+
+
+

### 2022-12-04 R/Process_functions.R
add script for long performance

@@ -267,4 +267,11 @@ get_matched_df = function(df, comps_dates,
 
 
 
+#' This functions cleans the dirty dataframe
+#'
+clean_df = function(dirty_df){
 
+
+
+
+}

### 2022-12-05 R/Auxilary_functions.R
add calculate_cumulative_return function and upadate script

@@ -85,3 +85,31 @@ pivot_to_join_format = function(match_table){
 
 
 }
+
+
+#' This function calculates cumulative gross and adjusted return
+#'
+calculate_cumulative_return = function(price_df, index_df, horizon){
+
+  price_df = price_df %>%
+    group_by(tase_id, sec_id) %>%
+    mutate(trade_duration = date - min(date)) %>%
+    ungroup()
+
+  ret_df = price_df %>%
+    left_join(index_df, by = "date") %>%
+    group_by(tase_id, sec_id) %>%
+    filter(trade_duration == 0 |
+             trade_duration %in% (horizon + + c(-3:3))) %>%
+    slice(1, length(date)) %>%
+    arrange(date) %>%
+    summarise(sec_ret = (close[2] / close[1] - 1),
+              sec_ret_adj = (close[2] / close[1] - 1) -
+                            (index[2] / index[1] - 1),
+              .groups = "drop")
+
+  return(ret_df)
+
+
+
+}

### 2022-12-10 R/Auxilary_functions.R
add data validation and desc stats

@@ -113,3 +113,28 @@ calculate_cumulative_return = function(price_df, index_df, horizon){
 
 
 }
+
+
+#' This function mutates the price data
+#'
+clean_price_data = function(price_vec){
+
+  power_vec = floor(log10(price_vec))
+
+  diff_power_vec = diff(power_vec)
+
+  break_index = which(diff_power_vec == max(diff_power_vec))
+
+  price_vec[1: break_index] = price_vec[1: break_index] * 10 ^ max(diff_power_vec)
+
+  10 ^ power_vec
+
+  price_vec * (10 ^ (-power_vec))
+
+
+
+
+
+
+}
+

### 2022-12-12 R/Import_functions.R
filter outliers and plot long run performance

@@ -99,7 +99,6 @@ import_boi_market_data = function(filepath){
     rename_all(tolower) %>%
     rename(tase_id = tase_issuer_id,
            sec_id = security_ident_num_tase,
-           close = close_rate_adj,
            date = date_value) %>%
     mutate(date = as_date(date)) %>%
     mutate(sec_id = as.character(as.numeric(sec_id)))
@@ -107,7 +106,6 @@ import_boi_market_data = function(filepath){
 
   df = df %>%
     mutate(across(-c(sec_id,tase_id, date), as.numeric))
-
 
 
   return(df)

### 2022-12-12 R/Process_functions.R

@@ -267,9 +267,22 @@ get_matched_df = function(df, comps_dates,
 
 
 
-#' This functions cleans the dirty dataframe
+#' This functions calculates adjusted price
 #'
-clean_df = function(dirty_df){
+calculate_adjusted_price = function(df,
+                                    base_rate_threshold = 1){
+
+  adjusted_df = df %>%
+    filter(!is.na(base_rate)) %>%
+    group_by(tase_id, sec_id) %>%
+    filter(abs(base_rate -  base_rate_threshold) > 0.1) %>%
+    arrange(date) %>%
+    mutate(daily_gross_ret = close_rate / base_rate) %>%
+    mutate(close_adjusted = close_rate[1] * c(1,cumprod(daily_gross_ret)[-1])) %>%
+    ungroup()
+
+  return(adjusted_df)
+
 
 
 

### 2022-12-24 R/Auxilary_functions.R
add presentation and preprocessing to functions

@@ -87,30 +87,65 @@ pivot_to_join_format = function(match_table){
 }
 
 
-#' This function calculates cumulative gross and adjusted return
+#' This function calculates raw and adjusted return
 #'
-calculate_cumulative_return = function(price_df, index_df, horizon){
-
-  price_df = price_df %>%
-    group_by(tase_id, sec_id) %>%
-    mutate(trade_duration = date - min(date)) %>%
-    ungroup()
+calculate_return_df = function(price_df){
 
   ret_df = price_df %>%
-    left_join(index_df, by = "date") %>%
-    group_by(tase_id, sec_id) %>%
-    filter(trade_duration == 0 |
-             trade_duration %in% (horizon + + c(-3:3))) %>%
-    slice(1, length(date)) %>%
-    arrange(date) %>%
-    summarise(sec_ret = (close[2] / close[1] - 1),
-              sec_ret_adj = (close[2] / close[1] - 1) -
-                            (index[2] / index[1] - 1),
-              .groups = "drop")
+    group_by(id) %>%
+    arrange(month) %>%
+    mutate(across(c("close","index", "control"),
+                  ~ . /lag(.) - 1,
+                  .names = "{.col}_ret")) %>%
+    ungroup() %>%
+    select(-c("close","index","control"))
 
-  return(ret_df)
+  adj_ret_df = ret_df %>%
+    pivot_longer(c("index_ret","control_ret"),
+                 names_to = "benchmark",
+                 values_to = "benchmark_ret") %>%
+    filter(complete.cases(.)) %>%
+    mutate(adjusted_ret = close_ret - benchmark_ret) %>%
+    select(-benchmark_ret) %>%
+    pivot_wider(names_from = "benchmark",
+                values_from = "adjusted_ret") %>%
+    pivot_longer(-c(id,month),names_to = "adjustment_type")
 
 
+  return(adj_ret_df)
+
+
+}
+
+
+#' This function calculates cumulative return
+#'
+calculate_cum_return = function(ret_df){
+
+  avg_adj_ret_df = ret_df%>%
+    group_by(month, adjustment_type) %>%
+    summarise(across(value,
+                     .fns = list(mean = ~mean(.,na.rm = TRUE),
+                                 median = ~median(.,na.rm = TRUE)),
+                     .names = "{.fn}"), .groups = "drop")
+
+
+  cum_ret_df = avg_adj_ret_df  %>%
+    filter(month <= 120)  %>%
[…]

### 2022-12-24 R/Process_functions.R

@@ -180,91 +180,55 @@ make_reg_df = function(market_df, finrep_df,
 
 
 #' This function matches delisted and control companies by
-#' selected varible
-#'
-#' @param comps_list table with tase_ id, ipo_date, delisted_status
-#'
-#' @param matching_variable the variable control group is matched on
-#'
+#' sector and market cap
 #' @param threshold allowed percentage difference between delisted
 #'  and control comps
 #'
 #'
-match_control_group = function(comps_list, data_df,
-                               matching_variable,
-                               threshold){
+match_control_group = function(market_df, tase_sector_df,
+                               stocks_ipo,threshold = 0.1){
 
-  data_df = data_df %>%
-    select(tase_id, date, all_of(matching_variable)) %>%
-    filter(complete.cases(.))
+  ipo_control_match_df = market_df %>%
+    select(tase_id, sec_id, date, market_value) %>%
+    inner_join(stocks_ipo %>%
+                 select(tase_id), by = "tase_id") %>%
+    group_by(tase_id, sec_id) %>%
+    summarise(first_date = date[date == min(date)],
+              first_market_value = market_value[date == min(date)],
+              .groups = "drop") %>%
+    filter(!is.na(first_market_value)) %>%
+    mutate(date = as.yearmon(first_date)) %>%
+    left_join(tase_sector_df, by = c("tase_id","date")) %>%
+    filter(!is.na(tase_sector)) %>%
+    unite(id, tase_id:sec_id)
 
-  delisted_comps= comps_list %>%
-    filter(delisted_status == 1) %>%
-    select(tase_id, ipo_date) %>%
-    mutate(tase_id = as.character(tase_id)) %>%
-    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
-    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
-    filter(complete.cases(.))
-
-
-  control_comps = comps_list %>%
-    filter(delisted_status == 0) %>%
-    select(tase_id, ipo_date) %>%
-    mutate(tase_id = as.character(tase_id)) %>%
-    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
-    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
-    filter(complete.cases(.))
-
-  del_var = paste0(matching_variable,"_delisted")
-
-  control_var = paste0(matching_variable,"_control")
[…]

### 2022-12-25 R/Auxilary_functions.R
add holding periods returns calculation  + update functions

@@ -122,7 +122,7 @@ calculate_return_df = function(price_df){
 #'
 calculate_cum_return = function(ret_df){
 
-  avg_adj_ret_df = ret_df%>%
+  avg_adj_ret_df = ret_df %>%
     group_by(month, adjustment_type) %>%
     summarise(across(value,
                      .fns = list(mean = ~mean(.,na.rm = TRUE),
@@ -146,6 +146,28 @@ calculate_cum_return = function(ret_df){
     ungroup()
 
   return(cum_ret_df)
+
+}
+
+
+#' This function calculates holding return
+#'
+calculate_holding_return = function(ret_df){
+
+  three_year_id = ret_df %>%
+    group_by(id, adjustment_type) %>%
+    summarise(len = length(month), .groups = "drop") %>%
+    filter(len >= 36) %>%
+    select(id)
+
+  hold_ret = ret_df %>%
+    inner_join(three_year_id, by = "id") %>%
+    filter(month <= 36) %>%
+    group_by(id,adjustment_type) %>%
+    summarise(hold_ret = prod(1 + value) - 1, .groups = "drop")
+
+
+  return(hold_ret)
 
 }
 

### 2022-12-25 R/Auxilary_functions.R
update box

@@ -87,30 +87,88 @@ pivot_to_join_format = function(match_table){
 }
 
 
-#' This function calculates cumulative gross and adjusted return
+#' This function calculates raw and adjusted return
 #'
-calculate_cumulative_return = function(price_df, index_df, horizon){
-
-  price_df = price_df %>%
-    group_by(tase_id, sec_id) %>%
-    mutate(trade_duration = date - min(date)) %>%
-    ungroup()
+calculate_return_df = function(price_df){
 
   ret_df = price_df %>%
-    left_join(index_df, by = "date") %>%
-    group_by(tase_id, sec_id) %>%
-    filter(trade_duration == 0 |
-             trade_duration %in% (horizon + + c(-3:3))) %>%
-    slice(1, length(date)) %>%
-    arrange(date) %>%
-    summarise(sec_ret = (close[2] / close[1] - 1),
-              sec_ret_adj = (close[2] / close[1] - 1) -
-                            (index[2] / index[1] - 1),
-              .groups = "drop")
+    group_by(id) %>%
+    arrange(month) %>%
+    mutate(across(c("close","index", "control"),
+                  ~ . /lag(.) - 1,
+                  .names = "{.col}_ret")) %>%
+    ungroup() %>%
+    select(-c("close","index","control"))
 
-  return(ret_df)
+  adj_ret_df = ret_df %>%
+    pivot_longer(c("index_ret","control_ret"),
+                 names_to = "benchmark",
+                 values_to = "benchmark_ret") %>%
+    filter(complete.cases(.)) %>%
+    mutate(adjusted_ret = close_ret - benchmark_ret) %>%
+    select(-benchmark_ret) %>%
+    pivot_wider(names_from = "benchmark",
+                values_from = "adjusted_ret") %>%
+    pivot_longer(-c(id,month),names_to = "adjustment_type")
 
 
+  return(adj_ret_df)
+
+
+}
+
+
+#' This function calculates cumulative return
+#'
+calculate_cum_return = function(ret_df){
+
+  avg_adj_ret_df = ret_df %>%
+    group_by(month, adjustment_type) %>%
+    summarise(across(value,
+                     .fns = list(mean = ~mean(.,na.rm = TRUE),
+                                 median = ~median(.,na.rm = TRUE)),
+                     .names = "{.fn}"), .groups = "drop")
+
+
+  cum_ret_df = avg_adj_ret_df  %>%
[…]

### 2022-12-25 R/Process_functions.R

@@ -180,84 +180,73 @@ make_reg_df = function(market_df, finrep_df,
 
 
 #' This function matches delisted and control companies by
-#' selected varible
-#'
-#' @param comps_list table with tase_ id, ipo_date, delisted_status
-#'
-#' @param matching_variable the variable control group is matched on
-#'
+#' sector and market cap
 #' @param threshold allowed percentage difference between delisted
 #'  and control comps
 #'
 #'
-match_control_group = function(comps_list, data_df,
-                               matching_variable,
-                               threshold){
+match_control_group = function(market_df, tase_sector_df,
+                               stocks_ipo,threshold = 0.1){
 
-  data_df = data_df %>%
-    select(tase_id, date, all_of(matching_variable)) %>%
-    filter(complete.cases(.))
+  ipo_control_match_df = market_df %>%
+    select(tase_id, sec_id, date, market_value) %>%
+    inner_join(stocks_ipo %>%
+                 select(tase_id), by = "tase_id") %>%
+    group_by(tase_id, sec_id) %>%
+    summarise(first_date = date[date == min(date)],
+              first_market_value = market_value[date == min(date)],
+              .groups = "drop") %>%
+    filter(!is.na(first_market_value)) %>%
+    mutate(date = as.yearmon(first_date)) %>%
+    left_join(tase_sector_df, by = c("tase_id","date")) %>%
+    filter(!is.na(tase_sector)) %>%
+    unite(id, tase_id:sec_id)
 
-  delisted_comps= comps_list %>%
-    filter(delisted_status == 1) %>%
-    select(tase_id, ipo_date) %>%
-    mutate(tase_id = as.character(tase_id)) %>%
-    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
-    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
-    filter(complete.cases(.))
-
-
-  control_comps = comps_list %>%
-    filter(delisted_status == 0) %>%
-    select(tase_id, ipo_date) %>%
-    mutate(tase_id = as.character(tase_id)) %>%
-    mutate(ipo_date = as.yearqtr(ipo_date)) %>%
-    left_join(data_df, by = c("tase_id", "ipo_date" = "date")) %>%
-    filter(complete.cases(.))
-
-  del_var = paste0(matching_variable,"_delisted")
-
-  control_var = paste0(matching_variable,"_control")
[…]

### 2022-12-26 R/Auxilary_functions.R
bugfix calculate_holding_returns + update presentation examples

@@ -155,7 +155,8 @@ calculate_cum_return = function(ret_df){
 calculate_holding_return = function(ret_df){
 
   three_year_id = ret_df %>%
-    group_by(id, adjustment_type) %>%
+    filter(adjustment_type == "close_ret") %>%
+    group_by(id) %>%
     summarise(len = length(month), .groups = "drop") %>%
     filter(len >= 36) %>%
     select(id)

### 2022-12-26 R/Auxilary_functions.R
bugfix calculate_holding_return

@@ -155,11 +155,11 @@ calculate_cum_return = function(ret_df){
 calculate_holding_return = function(ret_df){
 
   three_year_id = ret_df %>%
-    group_by(id, adjustment_type) %>%
+    filter(adjustment_type == "close_ret") %>%
+    group_by(id) %>%
     summarise(len = length(month), .groups = "drop") %>%
     filter(len >= 36) %>%
-    select(id) %>%
-    distinct()
+    select(id)
 
   hold_ret = ret_df %>%
     inner_join(three_year_id, by = "id") %>%

### 2022-12-28 R/Auxilary_functions.R
add cumulative returns plot

@@ -1,91 +1,3 @@
-#' @title Calculate Amihud's iiliquidity ratio
-#'
-#' @description This function calculates Amihud's iiliquidity ratio from market data
-#'
-#' @import dplyr
-#'
-#' @import zoo
-#'
-#' @param market_df a data frame with price and turnover data at daily frequency
-
-calculate_illiq = function(market_df){
-
-  market_df = market_df %>%
-    arrange(date)
-
-  illiq_df = market_df %>%
-    select(date, sec_id, close, turnover) %>%
-    group_by(sec_id) %>%
-    mutate(sec_ret = c(NA,diff(log(close)))) %>%
-    ungroup() %>%
-    filter(complete.cases(.)) %>%
-    mutate(daily_ratio = abs(sec_ret) / turnover) %>%
-    group_by(sec_id, date_yearmon = as.yearmon(date)) %>%
-    summarise(illiq = mean(sqrt(na.omit(daily_ratio))),
-              .groups = "drop")
-
-  return(illiq_df)
-
-}
-
-
-#' This function calculates betas and CAR's
-#'
-#' @import dplyr
-#'
-#' @import lubridate
-
-calculate.beta.and.car = function(df){
-
-  ta135 = read_csv(paste0(
-    file.path(Sys.getenv("USERPROFILE"), fsep = "\\"),
-    "\\OneDrive - Bank Of Israel\\Data\\",
-    "TASE liquidity\\TA_125_2000_2020.csv")) %>%
-    mutate(date = dmy(date))
-
-
-
-
-
-
-}
-
-
-
-#' This function pivots delisted and control comps into
-#' tase_id, date, comp_type format
-#'
-#' @param match_table a data frame with tase_id_delisted,
-#' tase_id_control, ipo_date, delisting_date structure
-#'
-pivot_to_join_format = function(match_table){
-
-  join_format = match_table %>%
-    mutate(time_period = map2(ipo_date, delisting_date,
-                              function(start,end){
-
-                                period = seq.Date(from = start,
-                                                  to = end,
-                                                  by = "quarter") %>%
-                                  as.yearqtr()
-
-                                return(period)
-
-
-                              })) %>%
-    select(starts_with("tase_id"), time_period) %>%
-    pivot_longer(starts_with("tase_id"),
-                 names_to = "comp_type", values_to = "tase_id") %>%
[…]

### 2022-12-28 R/Process_functions.R

@@ -1,103 +1,3 @@
-#' This function prepares the financial reports variables
-#'
-#' @import dplyr
-#'
-make_finrep_df = function(raw_df, selected_x_vars = NULL,
-                          filter_df = FALSE){
-
-  x_vars = c(
-    "leverage",
-    "capex_to_revenue",
-    "roa",
-    "free_cashflow",
-    "intangible"
-  )
-
-  finrep_df = raw_df %>%
-    rename_all(tolower)
-
-  finrep_df = finrep_df %>%
-    select(-starts_with("entity")) %>%
-    mutate(across(-c(starts_with("tase"),"year") &
-                    where(is.character),
-                  as.numeric)) %>%
-    mutate(leverage = total_liabilities / total_assets) %>%
-    mutate(capex_to_revenue = capex_cashflow / revenue) %>%
-    mutate(roa = operating_profit / total_assets) %>%
-    mutate(free_cashflow = operating_cashflow / total_assets)
-
-
-  if(!is.null(selected_x_vars)){
-
-    finrep_df = finrep_df %>%
-      select(date, tase_id, any_of(selected_x_vars))
-
-  }
-
-
-
-  if(filter_df){
-
-    finrep_df = finrep_df %>%
-      filter(complete.cases(.)) %>%
-      filter(across(where(is.numeric), is.finite))
-
-  }
-
-
-  return(finrep_df)
-
-
-
-
-
-
-}
-
-
-#' @title Prepare financial reports data
-#'
-#' @details This function prepares the financial reports
-#' variables data from Oracle format. The original values are given in thousands ILS
-#' and are scaled down by 1000 so that the result is in millions ILS
-#'
-#' @import dplyr
-#'
-make_finrep_oracle_df = function(raw_oracle_df,
-                                 raw_finrep_vars,
-                                 final_finrep_vars){
-
-
-  finrep_df = raw_oracle_df %>%
-    select(tase_id, date = date_yearqtr, any_of(raw_finrep_vars))
-
-  finrep_df = finrep_df %>%
-    mutate(across(-c("tase_id", "date"),as.numeric))
-
-  finrep_df = finrep_df %>%
-    mutate(across(where(is.numeric), ~ . * 10 ^ (-3)))
-
-  finrep_df = finrep_df %>%
-    mutate(leverage = total_liabilities / total_assets) %>%
-    mutate(capex_to_revenue =
-             investing_activities / total_revenue) %>%
[…]

### 2023-01-01 R/Auxilary_functions.R
update cumulative abnormal returns part

@@ -36,7 +36,8 @@ calculate_cum_return = function(ret_df){
 
   avg_adj_ret_df = ret_df %>%
     group_by(month, adjustment_type) %>%
-    summarise(value = mean(value, na.rm = TRUE), .groups = "drop")
+    summarise(value = mean(value, na.rm = TRUE),
+              comps_num = length(id), .groups = "drop")
 
 
   cum_ret_df = avg_adj_ret_df  %>%

### 2023-01-01 R/Process_functions.R

@@ -93,6 +93,65 @@ match_control_group = function(market_df, tase_sector_df,
 }
 
 
+#' This function matches delisted and control companies by
+#' sector and annualiesed market cap
+#' @param threshold allowed percentage difference between delisted
+#'  and control comps
+#'
+#'
+match_control_group_annual_mcap = function(market_df, tase_sector_df,
+                               stocks_ipo,threshold = 0.1){
+
+  tase_sector_df = tase_sector_df %>%
+    mutate(year = year(date)) %>%
+    select(year,tase_id, tase_sector) %>%
+    distinct()
+
+  ipo_control_match_df = market_df %>%
+    select(tase_id, sec_id, date, market_value) %>%
+    inner_join(stocks_ipo %>%
+                 select(tase_id), by = "tase_id") %>%
+    mutate(year = year(date)) %>%
+    group_by(tase_id, sec_id) %>%
+    filter(year == min(year)) %>%
+    group_by(tase_id, sec_id, year) %>%
+    summarise(market_value = mean(market_value, na.rm = TRUE),
+              .groups = "drop") %>%
+    filter(!is.na(market_value)) %>%
+    left_join(tase_sector_df, by = c("tase_id","year")) %>%
+    filter(!is.na(tase_sector)) %>%
+    unite(id, tase_id:sec_id)
+
+  target_market_df = market_df %>%
+    mutate(year = year(date)) %>%
+    group_by(tase_id, sec_id, year) %>%
+    summarise(market_value = mean(market_value, na.rm = TRUE),
+              .groups = "drop") %>%
+    filter(complete.cases(.)) %>%
+    left_join(tase_sector_df, by = c("tase_id","year")) %>%
+    unite(id, tase_id:sec_id)
+
+
+
+  matched_df = ipo_control_match_df %>%
+     left_join(target_market_df,
+              by = c("year", "tase_sector"),
+              suffix = c("_ipo","_control")) %>%
+    group_by(id_ipo) %>%
+    mutate(value_diff = abs(market_value_ipo / market_value_control - 1)) %>%
+    arrange(value_diff) %>%
+    slice(2) %>%
+    ungroup() %>%
+    filter(value_diff <= threshold)
+
+
+  return(matched_df)
+
+
+}
+
+
+
 #' This functions calculates adjusted price
 #'
 calculate_adjusted_price = function(df,
@@ -153,4 +212,5 @@ make_price_df = function(market_df,ipo_control_match_df,ta_125 ){
 
 
 }
+
 

### 2023-01-01 R/Auxilary_functions.R
add holding returns

@@ -10,7 +10,18 @@ calculate_return_df = function(price_df){
                   ~ . /lag(.) - 1,
                   .names = "{.col}_ret")) %>%
     ungroup() %>%
-    select(-c("close","index","control"))
+    select(-c("close","index","control")) %>%
+    filter(complete.cases(.))
+
+  return(ret_df)
+
+
+}
+
+
+#' This function calculates cumulative return
+#'
+calculate_cum_return = function(ret_df){
 
   adj_ret_df = ret_df %>%
     pivot_longer(c("index_ret","control_ret"),
@@ -23,21 +34,10 @@ calculate_return_df = function(price_df){
                 values_from = "adjusted_ret") %>%
     pivot_longer(-c(id,month),names_to = "adjustment_type")
 
-
-  return(adj_ret_df)
-
-
-}
-
-
-#' This function calculates cumulative return
-#'
-calculate_cum_return = function(ret_df){
-
-  avg_adj_ret_df = ret_df %>%
+  avg_adj_ret_df = adj_ret_df %>%
     group_by(month, adjustment_type) %>%
     summarise(value = mean(value, na.rm = TRUE),
-              comps_num = length(id), .groups = "drop")
+              num_comps = length(id), .groups = "drop")
 
 
   cum_ret_df = avg_adj_ret_df  %>%
@@ -63,18 +63,19 @@ calculate_cum_return = function(ret_df){
 #'
 calculate_holding_return = function(ret_df){
 
-  three_year_id = ret_df %>%
-    filter(adjustment_type == "close_ret") %>%
-    group_by(id) %>%
-    summarise(len = length(month), .groups = "drop") %>%
-    filter(len >= 36) %>%
-    select(id)
+ hold_ret = ret_df %>%
+   group_by(id) %>%
+   arrange(month) %>%
+   mutate(across(ends_with("ret"),~ cumprod(1 + .) - 1)) %>%
+   ungroup()
 
-  hold_ret = ret_df %>%
-    inner_join(three_year_id, by = "id") %>%
-    filter(month <= 36) %>%
-    group_by(id,adjustment_type) %>%
-    summarise(hold_ret = prod(1 + value) - 1, .groups = "drop")
+ hold_ret =  hold_ret %>%
+   group_by(month) %>%
+   summarise(across(ends_with("ret"), ~mean(., na.rm = TRUE)),
+             num_comps = length(id),
+             .groups = "drop") %>%
[…]

### 2023-01-02 R/Process_functions.R
add tase sector to price df

@@ -178,7 +178,8 @@ calculate_adjusted_price = function(df,
 #' This function makes price df by joining price data for securities and
 #' benchmarks
 #'
-make_price_df = function(market_df,ipo_control_match_df,ta_125 ){
+make_price_df = function(market_df,ipo_control_match_df,ta_125,
+                         tase_sector_df){
 
   benchmark_df =  market_df %>%
     select(tase_id, sec_id,date, control = close_adjusted) %>%
@@ -190,11 +191,21 @@ make_price_df = function(market_df,ipo_control_match_df,ta_125 ){
 
 
   price_df = market_df %>%
-    select(tase_id, sec_id,date, close = close_adjusted) %>%
     inner_join(stocks_ipo %>%
-                 select(tase_id),by = "tase_id") %>%
+                 select(tase_id),by = "tase_id")
+
+  price_df = price_df %>%
+    select(tase_id, sec_id,date, close = close_adjusted) %>%
+    mutate(date_yearmon = as.yearmon(date)) %>%
+    left_join(tase_sector_df,
+              by = c("date_yearmon" = "date", "tase_id")) %>%
+    select(-date_yearmon)
+
+  price_df = price_df %>%
     left_join(ta_125 %>%
-                rename(index = ta_125), by = "date") %>%
+                rename(index = ta_125), by = "date")
+
+  price_df = price_df %>%
     mutate(id = paste(tase_id, sec_id, sep = "_")) %>%
     left_join(benchmark_df,by = c("date", "id")) %>%
     select(-c(tase_id,sec_id,id_control))
@@ -205,6 +216,7 @@ make_price_df = function(market_df,ipo_control_match_df,ta_125 ){
     mutate(month = as.numeric(date - date[date == min(date)]) %/% 22) %>%
     group_by(id, month) %>%
     summarise(across(c("close","index","control"), ~mean(., na.rm = TRUE)),
+              tase_sector = unique(tase_sector),
               .groups = "drop")
 
   return(price_df)

### 2023-01-02 R/Auxilary_functions.R
attempt to add sector - not working

@@ -24,6 +24,8 @@ calculate_return_df = function(price_df){
 calculate_cum_return = function(ret_df){
 
   adj_ret_df = ret_df %>%
+    select(-any_of("tase_sector")) %>%
+    distinct() %>%
     pivot_longer(c("index_ret","control_ret"),
                  names_to = "benchmark",
                  values_to = "benchmark_ret") %>%

### 2023-01-16 R/Auxilary_functions.R
update article and add data validation example

@@ -11,17 +11,16 @@ calculate_return_df = function(price_df){
                   .names = "{.col}_ret")) %>%
     ungroup() %>%
     select(-c("close","index","control")) %>%
-    filter(complete.cases(.))
+    filter(!is.na(close_ret))
 
   return(ret_df)
 
 
 }
 
-
-#' This function calculates cumulative return
+#' This function adjustes (removes) for benchmark
 #'
-calculate_cum_return = function(ret_df){
+adjust_returns_to_benchmark = function(ret_df){
 
   adj_ret_df = ret_df %>%
     pivot_longer(c("index_ret","control_ret"),
@@ -34,6 +33,29 @@ calculate_cum_return = function(ret_df){
                 values_from = "adjusted_ret") %>%
     pivot_longer(-c(id,month),names_to = "adjustment_type")
 
+  adj_ret_df = adj_ret_df %>%
+    mutate(adjustment_type = factor(
+      adjustment_type,
+      levels = c("close_ret", "index_ret", "control_ret"),
+      labels = c(
+        "Raw returns",
+        "Index adjusted returns",
+        "Control adjusted returns"
+      )
+    ))
+
+  return(adj_ret_df)
+
+
+
+}
+
+#' This function calculates cumulative return
+#'
+calculate_cum_return = function(ret_df){
+
+  adj_ret_df = adjust_returns_to_benchmark(ret_df)
+
   avg_adj_ret_df = adj_ret_df %>%
     group_by(month, adjustment_type) %>%
     summarise(value = mean(value, na.rm = TRUE),
@@ -41,13 +63,7 @@ calculate_cum_return = function(ret_df){
 
 
   cum_ret_df = avg_adj_ret_df  %>%
-    filter(month <= 120)  %>%
-    mutate(adjustment_type = factor(
-      adjustment_type,
-      labels = c("Raw returns",
-                 "Abnormal (index adjusted) returns",
-                 "Control group returns")
-    )) %>%
+    filter(month <= 120) %>%
     filter(complete.cases(.)) %>%
     group_by(adjustment_type) %>%
     arrange(month) %>%
@@ -63,23 +79,51 @@ calculate_cum_return = function(ret_df){
 #'
 calculate_holding_return = function(ret_df){
 
- hold_ret = ret_df %>%
-   group_by(id) %>%
-   arrange(month) %>%
[…]

### 2023-01-16 R/Process_functions.R

@@ -202,7 +202,7 @@ make_price_df = function(market_df,ipo_control_match_df,ta_125 ){
 
   price_df = price_df %>%
     group_by(id) %>%
-    mutate(month = as.numeric(date - date[date == min(date)]) %/% 22) %>%
+    mutate(month = as.numeric(date - min(date)) %/% 22 + 1) %>%
     group_by(id, month) %>%
     summarise(across(c("close","index","control"), ~mean(., na.rm = TRUE)),
               .groups = "drop")

### 2023-02-01 R/Process_functions.R
add daily bhar with one matched firm to robustness

@@ -157,6 +157,11 @@ match_control_group_annual_mcap = function(market_df, tase_sector_df,
 calculate_adjusted_price = function(df,
                                     base_rate_threshold = 1){
 
+  if("close_rate_adj" %in% names(df)){
+
+    df = df %>% select(-"close_rate_adj")
+  }
+
   adjusted_df = df %>%
     filter(!is.na(base_rate)) %>%
     group_by(tase_id, sec_id) %>%
@@ -164,7 +169,8 @@ calculate_adjusted_price = function(df,
     arrange(date) %>%
     mutate(daily_gross_ret = close_rate / base_rate) %>%
     mutate(close_adjusted = close_rate[1] * c(1,cumprod(daily_gross_ret)[-1])) %>%
-    ungroup()
+    ungroup() %>%
+    select(-daily_gross_ret)
 
   return(adjusted_df)
 
@@ -213,7 +219,7 @@ make_price_df = function(market_df,ipo_control_match_df,ta_125,
 
   price_df = price_df %>%
     group_by(id) %>%
-    mutate(month = as.numeric(date - date[date == min(date)]) %/% 22) %>%
+    mutate(month = as.numeric(date -  min(date)) %/% 22) %>%
     group_by(id, month) %>%
     summarise(across(c("close","index","control"), ~mean(., na.rm = TRUE)),
               tase_sector = unique(tase_sector),

### 2023-02-01 R/robustness_auxilary_functions.R

@@ -1,0 +1,34 @@
+
+#' This function takes returns df and mathed table and calculates
+#' benchmark performance
+#'
+#'
+#'
+
+calculate_benchmark_performance = function(returns_df, matched_sample,
+                                           target_duration){
+
+  ipo_returns_df = returns_df %>%
+    inner_join(select(matched_sample, "id_ipo"), by = c("id" = "id_ipo")) %>%
+    group_by(id) %>%
+    mutate(dur_diff = abs(duration - target_duration)) %>%
+    filter(dur_diff == min(dur_diff)) %>%
+    ungroup()
+
+  benchmark_performance_df = matched_sample %>%
+    left_join(ipo_returns_df, by = c("id_ipo" = "id")) %>%
+    left_join(returns_df, by = c("id_control" = "id"),
+              suffix = c("_ipo","_control"))
+
+  benchmark_performance_df = benchmark_performance_df %>%
+    mutate(duration_diff = abs(duration_ipo - duration_control)) %>%
+    select(-c("duration_ipo","duration_control")) %>%
+    group_by(id_control) %>%
+    filter(duration_diff == min(duration_diff)) %>%
+    ungroup() %>%
+    mutate(wealth_relative = (1 + bhar_ipo) / (1 + bhar_control)) %>%
+    select(contains("id"), contains("bhar"), wealth_relative, duration_diff)
+
+  return(benchmark_performance_df)
+
+}

### 2023-02-04 R/robustness_auxilary_functions.R
update lit review and move mathiching by size to different function

@@ -1,4 +1,58 @@
-#' This function matches
+#' This function matches comps by market value
+#'
+match_comps_by_market_value = function(ipo_comps, market_df,
+                                       age_threshold = 1,
+                                       market_threshold = 0.1,
+                                       single_match = TRUE){
+
+
+  ipo_sample = market_df %>%
+    filter(!is.na(market_value)) %>%
+    inner_join(ipo_comps, by = "tase_id") %>%
+    unite(id,c("tase_id","sec_id")) %>%
+    group_by(id) %>%
+    summarise(market_value = market_value[date == min(date)],
+              date = min(date),
+              .groups = "drop")
+
+  target_sample = market_df %>%
+    filter(!is.na(market_value)) %>%
+    unite(id, c("tase_id","sec_id")) %>%
+    select(date, id, market_value) %>%
+    group_by(id) %>%
+    mutate(age = as.numeric(date - min(date)) / 252) %>%
+    ungroup()
+
+
+  matched_sample = ipo_sample %>%
+    left_join(target_sample, by = c("date"),
+              suffix = c("_ipo","_control")) %>%
+    filter(complete.cases(.)) %>%
+    filter(age >= age_threshold) %>%
+    mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
+    filter(matching_diff < market_threshold)
+
+  if(single_match){
+
+    matched_sample = matched_sample %>%
+      group_by(id_ipo) %>%
+      slice_min(order_by = matching_diff) %>%
+      ungroup() %>%
+      select(id_ipo, id_control)
+
+
+  } else {
+
+    matched_sample = matched_sample %>%
+       select(id_ipo, id_control)
+
+
+  }
+
+ return(matched_sample)
+
+
+}
 
 
 

### 2023-02-15 R/robustness_auxilary_functions.R
bugfix match_comps_by_market_value

@@ -1,4 +1,9 @@
-#' This function matches comps by market value
+#' @title Match control comps to IPO comps
+#'
+#' @description This function matches control comps by market value
+#'
+#' @details The matching is performed on mature firms (\code{age_treshold}
+#' parameter)
 #'
 match_comps_by_market_value = function(ipo_comps, market_df,
                                        age_threshold = 1,
@@ -7,13 +12,13 @@ match_comps_by_market_value = function(ipo_comps, market_df,
 
 
   ipo_sample = market_df %>%
-    filter(!is.na(market_value)) %>%
     inner_join(ipo_comps, by = "tase_id") %>%
     unite(id,c("tase_id","sec_id")) %>%
     group_by(id) %>%
     summarise(market_value = market_value[date == min(date)],
               date = min(date),
-              .groups = "drop")
+              .groups = "drop") %>%
+    filter(complete.cases(.))
 
   target_sample = market_df %>%
     filter(!is.na(market_value)) %>%
@@ -21,14 +26,14 @@ match_comps_by_market_value = function(ipo_comps, market_df,
     select(date, id, market_value) %>%
     group_by(id) %>%
     mutate(age = as.numeric(date - min(date)) / 252) %>%
-    ungroup()
+    ungroup() %>%
+    filter(age >= age_threshold)
 
 
   matched_sample = ipo_sample %>%
     left_join(target_sample, by = c("date"),
               suffix = c("_ipo","_control")) %>%
     filter(complete.cases(.)) %>%
-    filter(age >= age_threshold) %>%
     mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
     filter(matching_diff < market_threshold)
 

### 2023-02-22 R/robustness_auxilary_functions.R
bugfix bhar calculation (average by id) and add period returns plot

@@ -87,3 +87,38 @@ calculate_bhar_from_price_df = function(price_df,
 
 
 }
+
+
+#' This function calculates periodic returns from price df. In order to do that
+#' the frequency is reduced by taking the endpoints of the period
+#'
+calculate_period_ret_from_price_df = function(price_df,
+                                                  period_freq,
+                                                  period_thresh = NULL){
+
+  period_df = price_df %>%
+    group_by(id,id_control) %>%
+    arrange(date) %>%
+    mutate(duration = as.numeric(date - min(date))) %>%
+    mutate(period = duration %/% period_freq) %>%
+    {if(!is.null(period_thresh)) filter(., period <= period_thresh) else .} %>%
+    group_by(period) %>%
+    slice_min(duration) %>%
+    ungroup()
+
+
+  ret_df = period_df %>%
+    group_by(id, id_control) %>%
+    arrange(period) %>%
+    mutate(across(starts_with("price"), ~. / lag(.) - 1)) %>%
+    ungroup() %>%
+    rename_with(.cols = starts_with("price"),
+                ~str_replace(.,"price","ret")) %>%
+    select(id, id_control,period, starts_with("ret")) %>%
+    filter(complete.cases(.)) %>%
+    mutate(ret_abnormal = ret_ipo - ret_control)
+
+  return(ret_df)
+
+
+}

### 2023-03-05 R/Auxilary_functions.R
update cumulative returns calculation

@@ -10,8 +10,7 @@ calculate_return_df = function(price_df){
                   ~ . /lag(.) - 1,
                   .names = "{.col}_ret")) %>%
     ungroup() %>%
-    select(-c("close","index","control")) %>%
-    filter(complete.cases(.))
+    select(-c("close","index","control"))
 
   return(ret_df)
 

### 2023-05-29 R/Import_functions.R
move matching functions to separate script

@@ -74,43 +74,6 @@ import.boi.finrep.data = function(filepath = NULL){
 }
 
 
-#' @title Import BoI format market report data
-#'
-#' @description  This function imports market data from BOI format
-#'
-#' @param filepath the path to financial report data (in csv format)
-#'
-#' @import dplyr
-#'
-#' @import readr
-#'
-#' @import lubridate
-#'
-#' @export
-
-
-import_boi_market_data = function(filepath){
-
-
-  temp_df = read_rds(filepath)
-
-
-  df = temp_df %>%
-    rename_all(tolower) %>%
-    rename(tase_id = tase_issuer_id,
-           sec_id = security_ident_num_tase,
-           date = date_value) %>%
-    mutate(date = as_date(date)) %>%
-    mutate(sec_id = as.character(as.numeric(sec_id)))
-
-
-  df = df %>%
-    mutate(across(-c(sec_id,tase_id, date), as.numeric))
-
-
-  return(df)
-
-}
 
 #' @title Import trading status data
 #'

### 2023-05-29 R/Process_functions.R

@@ -1,155 +1,33 @@
 
-#' This function prepares the market variable variables
+#' This function cleans market df and filters out irrelevant data
 #'
-#' @import dplyr
+#' @param market_df a data frame with the following structure:
+#'  date,tase_id,sec_id,close_adjusted,market_value
 #'
-#' @import slider
-#'
-make_market_df = function(df){
+clean_market_df = function(market_df){
 
-  # illiq_df = df %>%
-  #   calculate_illiq() %>%
-  #   group_by(tase_id, sec_id, date = as.yearqtr(date_yearmon)) %>%
-  #   summarise(illiq = mean(illiq, na.rm = TRUE), .groups = "drop")
-
-  sd_df = df %>%
-    select(tase_id, sec_id,date, close) %>%
-    group_by(tase_id, sec_id) %>%
-    arrange(date) %>%
-    mutate(ret = c(NA,diff(log(close)))) %>%
-    group_by(tase_id, sec_id, date = as.yearqtr(date)) %>%
-    summarise(volatility = sd(ret, na.rm = TRUE), .groups = "drop")
+  duplicated_comps = market_df %>%
+    select(tase_id, sec_id) %>%
+    distinct() %>%
+    count(tase_id) %>%
+    filter(n > 1)
 
 
-  market_df = df %>%
-    mutate(across(c(market_value, turnover),
-                  ~ . * 10 ^ (-6))) %>%
-    mutate(size = log(market_value)) %>%
-    group_by(tase_id, sec_id, date = as.yearqtr(date)) %>%
-    summarise(across(c(size, market_value, turnover, volume),
-                     mean, na.rm = TRUE), .groups = "drop")
+  market_df = market_df %>%
+    anti_join(duplicated_comps, by = "tase_id")
 
- market_df = market_df %>%
-   # full_join(illiq_df, by = c("sec_id","date")) %>%
-   full_join(sd_df, by = c("tase_id", "sec_id","date"))
+  market_df = market_df %>%
+    filter(!tase_id == 106)
 
 
- return(market_df)
+  market_df = market_df %>%
+    select(-sec_id) %>%
+    rename(price = close_adjusted)
 
+
+  return(market_df)
 
 }
-
-
-
-#' This function matches delisted and control companies by
-#' sector and market cap
-#' @param threshold allowed percentage difference between delisted
-#'  and control comps
-#'
-#'
-match_control_group = function(market_df, tase_sector_df,
-                               stocks_ipo,threshold = 0.1){
-
[…]

### 2023-05-29 R/matching_functions.R

@@ -1,0 +1,60 @@
+#' @title Match control comps to IPO comps
+#'
+#' @description This function matches control comps by market value
+#'
+#' @details The matching is performed on mature firms (\code{age_treshold}
+#' parameter)
+#'
+match_comps_by_market_value = function(ipo_comps, market_df,
+                                       age_threshold = 1,
+                                       market_threshold = 0.1,
+                                       single_match = TRUE){
+
+
+  ipo_sample = market_df %>%
+    inner_join(ipo_comps, by = "id") %>%
+    group_by(id) %>%
+    summarise(market_value = market_value[date == min(date)],
+              date = min(date),
+              .groups = "drop") %>%
+    filter(complete.cases(.))
+
+  target_sample = market_df %>%
+    filter(!is.na(market_value)) %>%
+    select(date, id, market_value) %>%
+    group_by(id) %>%
+    mutate(age = as.numeric(date - min(date)) / 252) %>%
+    ungroup() %>%
+    filter(age >= age_threshold)
+
+
+  matched_sample = ipo_sample %>%
+    left_join(target_sample, by = c("date"),
+              suffix = c("_ipo","_control"),
+              relationship = "many-to-many") %>%
+    filter(complete.cases(.)) %>%
+    mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
+    filter(matching_diff < market_threshold)
+
+  if(single_match){
+
+    matched_sample = matched_sample %>%
+      group_by(id_ipo) %>%
+      slice_min(order_by = matching_diff) %>%
+      ungroup() %>%
+      select(id_ipo, id_control)
+
+
+  } else {
+
+    matched_sample = matched_sample %>%
+      select(id_ipo, id_control)
+
+
+  }
+
+  return(matched_sample)
+
+
+}
+

### 2023-05-29 R/robustness_auxilary_functions.R

@@ -12,8 +12,7 @@ match_comps_by_market_value = function(ipo_comps, market_df,
 
 
   ipo_sample = market_df %>%
-    inner_join(ipo_comps, by = "tase_id") %>%
-    unite(id,c("tase_id","sec_id")) %>%
+    inner_join(ipo_comps, by = "id") %>%
     group_by(id) %>%
     summarise(market_value = market_value[date == min(date)],
               date = min(date),
@@ -22,7 +21,6 @@ match_comps_by_market_value = function(ipo_comps, market_df,
 
   target_sample = market_df %>%
     filter(!is.na(market_value)) %>%
-    unite(id, c("tase_id","sec_id")) %>%
     select(date, id, market_value) %>%
     group_by(id) %>%
     mutate(age = as.numeric(date - min(date)) / 252) %>%
@@ -32,7 +30,8 @@ match_comps_by_market_value = function(ipo_comps, market_df,
 
   matched_sample = ipo_sample %>%
     left_join(target_sample, by = c("date"),
-              suffix = c("_ipo","_control")) %>%
+              suffix = c("_ipo","_control"),
+              relationship = "many-to-many") %>%
     filter(complete.cases(.)) %>%
     mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
     filter(matching_diff < market_threshold)
@@ -68,7 +67,8 @@ match_comps_by_market_value = function(ipo_comps, market_df,
 #'
 
 calculate_bhar_from_price_df = function(price_df,
-                                           target_duration){
+                                        target_duration,
+                                        duration_tolerance = 0.05){
 
   bhar_df = price_df %>%
     group_by(id, id_control) %>%
@@ -80,6 +80,11 @@ calculate_bhar_from_price_df = function(price_df,
               bhar_control = (price_control[2] / price_control[1]) - 1,
               bhar_abnormal = bhar_ipo - bhar_control,
               duration = duration[2], .groups = "drop")
+
+  bhar_df = bhar_df %>%
+    mutate(dur_diff = target_duration / duration - 1) %>%
+    filter(dur_diff <= duration_tolerance) %>%
+    select(-duration, -dur_diff)
 
 
   return(bhar_df)

### 2023-05-29 R/matching_functions.R
calculated bhar for index, size and book to market matching

@@ -5,25 +5,23 @@
 #' @details The matching is performed on mature firms (\code{age_treshold}
 #' parameter)
 #'
-match_comps_by_market_value = function(ipo_comps, market_df,
-                                       age_threshold = 1,
-                                       market_threshold = 0.1,
+match_by_target_value = function(ipo_comps, target_df,
+                                       age_threshold,
+                                       target_threshold = 0.1,
                                        single_match = TRUE){
 
 
-  ipo_sample = market_df %>%
+  ipo_sample = target_df %>%
     inner_join(ipo_comps, by = "id") %>%
     group_by(id) %>%
-    summarise(market_value = market_value[date == min(date)],
+    summarise(target_value = target_value[date == min(date)],
               date = min(date),
               .groups = "drop") %>%
     filter(complete.cases(.))
 
-  target_sample = market_df %>%
-    filter(!is.na(market_value)) %>%
-    select(date, id, market_value) %>%
+  target_sample = target_df %>%
     group_by(id) %>%
-    mutate(age = as.numeric(date - min(date)) / 252) %>%
+    mutate(age = as.numeric(date - min(date))) %>%
     ungroup() %>%
     filter(age >= age_threshold)
 
@@ -33,8 +31,8 @@ match_comps_by_market_value = function(ipo_comps, market_df,
               suffix = c("_ipo","_control"),
               relationship = "many-to-many") %>%
     filter(complete.cases(.)) %>%
-    mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
-    filter(matching_diff < market_threshold)
+    mutate(matching_diff = abs(target_value_ipo/target_value_control - 1)) %>%
+    filter(matching_diff < target_threshold)
 
   if(single_match){
 

### 2023-05-29 R/robustness_auxilary_functions.R

@@ -1,62 +1,3 @@
-#' @title Match control comps to IPO comps
-#'
-#' @description This function matches control comps by market value
-#'
-#' @details The matching is performed on mature firms (\code{age_treshold}
-#' parameter)
-#'
-match_comps_by_market_value = function(ipo_comps, market_df,
-                                       age_threshold = 1,
-                                       market_threshold = 0.1,
-                                       single_match = TRUE){
-
-
-  ipo_sample = market_df %>%
-    inner_join(ipo_comps, by = "id") %>%
-    group_by(id) %>%
-    summarise(market_value = market_value[date == min(date)],
-              date = min(date),
-              .groups = "drop") %>%
-    filter(complete.cases(.))
-
-  target_sample = market_df %>%
-    filter(!is.na(market_value)) %>%
-    select(date, id, market_value) %>%
-    group_by(id) %>%
-    mutate(age = as.numeric(date - min(date)) / 252) %>%
-    ungroup() %>%
-    filter(age >= age_threshold)
-
-
-  matched_sample = ipo_sample %>%
-    left_join(target_sample, by = c("date"),
-              suffix = c("_ipo","_control"),
-              relationship = "many-to-many") %>%
-    filter(complete.cases(.)) %>%
-    mutate(matching_diff = abs(market_value_ipo/market_value_control - 1)) %>%
-    filter(matching_diff < market_threshold)
-
-  if(single_match){
-
-    matched_sample = matched_sample %>%
-      group_by(id_ipo) %>%
-      slice_min(order_by = matching_diff) %>%
-      ungroup() %>%
-      select(id_ipo, id_control)
-
-
-  } else {
-
-    matched_sample = matched_sample %>%
-       select(id_ipo, id_control)
-
-
-  }
-
- return(matched_sample)
-
-
-}
 
 
 

### 2023-05-31 R/Import_functions.R
add car calculation

@@ -1,219 +1,0 @@
-#' @title Import BoI format financial report data
-#'
-#' @description  This function imports financial report data from BOI format
-#'
-#' @param filepath the path to financial report data (in csv format)
-#'
-#' @import dplyr
-#'
-#' @import xts
-
-import.boi.finrep.data = function(filepath = NULL){
-
-  if(is.null(filepath)){filepath = paste0(file.path(
-    Sys.getenv("USERPROFILE"),fsep="\\"),
-    "\\OneDrive - Bank Of Israel\\Data\\",
-    "TASE liquidity\\FinancialReports.csv")}
-
-  temp_df = read.csv(filepath, encoding = "UTF-8",
-                     header = FALSE,
-                     stringsAsFactors = FALSE)
-
-  names_vec = c(
-    "Year",
-    "Date",
-    "TASE_branch",
-    "TASE_ID",
-    "Entity_Name",
-    "Entity_ID",
-    "Total_Assets",
-    "Current_Assets",
-    "Cash_Equivalent",
-    "Non_Current_Assets",
-    "Total_Liabilities",
-    "Current_Liabilities",
-    "Non_current_Liabilities",
-    "Equity",
-    "Minority_rights",
-    "Revenue",
-    "Total_Cost",
-    "Operating_Profit",
-    "Financing_cost",
-    "Profit_before_tax",
-    "Tax",
-    "Net_Profit",
-    "Minority_Profit",
-    "Operating_CashFlow",
-    "Capex_CashFlow",
-    "Financial_CashFlow"
-  )
-
-  df = temp_df %>%
-    slice(-1) %>%
-    setNames(names_vec) %>%
-    mutate(Date = as.yearqtr(Date, format = "Q%q/%Y")) %>%
-    mutate(TASE_branch = factor(TASE_branch))
-
-  Sys.setlocale(locale = "hebrew")
-
-  levels(df$TASE_branch) = list(
-    "Biomed" = "ביומד",
-    "Insurance" = "ביטוח",
-    "Banks" = "בנקים",
-    "Investment_Holdings" = "השקעה ואחזקות",
-    "Technology" = "טכנולוגיה",
-    "Services" = "מסחר ושרותים",
-    "Real_estate" = "נדל\"ן ובינוי",
-    "Fin_services" = "שרותים פיננסיים",
-    "Industry" = "תעשיה"
-  )
-
-
-  return(df)
-
-}
-
-
-
-#' @title Import trading status data
-#'
-#' @description This function imports data set about listing status of TASE companies
-#'
[…]

### 2023-05-31 R/robustness_auxilary_functions.R

@@ -1,8 +1,6 @@
 
-
-
-#' This function takes returns df and mathed table and calculates
-#' benchmark performance
+#' This function calculates buy and hold returns from
+#' price df (matched ipo and control)
 #'
 #'
 #'
@@ -34,37 +32,56 @@ calculate_bhar_from_price_df = function(price_df,
 
 }
 
-
-#' This function calculates periodic returns from price df. In order to do that
-#' the frequency is reduced by taking the endpoints of the period
+#' This function calculates average abnormal returns from
+#' price df (matched ipo and control)
 #'
-calculate_period_ret_from_price_df = function(price_df,
-                                                  period_freq,
-                                                  period_thresh = NULL){
+average_abnormal_return = function(price_df){
 
-  period_df = price_df %>%
-    group_by(id,id_control) %>%
+  abnormal_df = price_df %>%
+    group_by(id, id_control) %>%
     arrange(date) %>%
-    mutate(duration = as.numeric(date - min(date))) %>%
-    mutate(period = duration %/% period_freq) %>%
-    {if(!is.null(period_thresh)) filter(., period <= period_thresh) else .} %>%
-    group_by(period) %>%
-    slice_min(duration) %>%
+    mutate(across(c("price_ipo","price_control"), ~./dplyr::lag(.) - 1)) %>%
+    ungroup() %>%
+    rename_with(~str_replace_all(.,"price","ret")) %>%
+    filter(complete.cases(.)) %>%
+    mutate(abnormal_return = ret_ipo - ret_control)
+
+  average_df = abnormal_df %>%
+    group_by(date) %>%
+    summarise(average_abnormal_return = mean(abnormal_return),
+              .groups = "drop")
+
+
+  return(average_df)
+
+
+
+}
+
+#' This function transforms price df into trading months
+#'
+convert_to_trading_months = function(price_df){
+
+  first_day_df = price_df %>%
+    group_by(id, id_control) %>%
+    filter(date == min(date)) %>%
+    mutate(date = 0)
+
+  monthly_df = price_df %>%
+    group_by(id, id_control) %>%
+    mutate(date = as.numeric(date - min(date))) %>%
+    filter(!date == 0) %>%
+    mutate(date = (date %/% 22) + 1) %>%
     ungroup()
 
+  monthly_df = monthly_df %>%
+    bind_rows(first_day_df) %>%
+    arrange(id,id_control, date)
[…]

### 2023-06-04 R/Auxilary_functions.R
add ctar calculation

@@ -1,131 +1,0 @@
-
-#' This function calculates raw and adjusted return
-#'
-calculate_return_df = function(price_df){
-
-  ret_df = price_df %>%
-    group_by(id) %>%
-    arrange(month) %>%
-    mutate(across(c("close","index", "control"),
-                  ~ . /lag(.) - 1,
-                  .names = "{.col}_ret")) %>%
-    ungroup() %>%
-    select(-c("close","index","control")) %>%
-    filter(!is.na(close_ret))
-
-  return(ret_df)
-
-
-}
-
-#' This function adjustes (removes) for benchmark
-#'
-adjust_returns_to_benchmark = function(ret_df){
-
-  adj_ret_df = ret_df %>%
-    select(-any_of("tase_sector")) %>%
-    distinct() %>%
-    pivot_longer(c("index_ret","control_ret"),
-                 names_to = "benchmark",
-                 values_to = "benchmark_ret") %>%
-    filter(complete.cases(.)) %>%
-    mutate(adjusted_ret = close_ret - benchmark_ret) %>%
-    select(-benchmark_ret) %>%
-    pivot_wider(names_from = "benchmark",
-                values_from = "adjusted_ret") %>%
-    pivot_longer(-c(id,month),names_to = "adjustment_type")
-
-  adj_ret_df = adj_ret_df %>%
-    mutate(adjustment_type = factor(
-      adjustment_type,
-      levels = c("close_ret", "index_ret", "control_ret"),
-      labels = c(
-        "Raw returns",
-        "Index adjusted returns",
-        "Control adjusted returns"
-      )
-    ))
-
-  return(adj_ret_df)
-
-
-
-}
-
-#' This function calculates cumulative return
-#'
-calculate_cum_return = function(ret_df){
-
-  adj_ret_df = adjust_returns_to_benchmark(ret_df)
-
-  avg_adj_ret_df = adj_ret_df %>%
-    group_by(month, adjustment_type) %>%
-    summarise(value = mean(value, na.rm = TRUE),
-              num_comps = length(id), .groups = "drop")
-
-
-  cum_ret_df = avg_adj_ret_df  %>%
-    filter(month <= 120) %>%
-    filter(complete.cases(.)) %>%
-    group_by(adjustment_type) %>%
-    arrange(month) %>%
-    mutate(value = cumsum(value)) %>%
-    ungroup()
-
-  return(cum_ret_df)
-
-}
-
[…]

### 2023-06-04 R/Process_functions.R

@@ -59,6 +59,30 @@ calculate_adjusted_price = function(df,
 }
 
 
+#' This functions makes a data frame with time series index of of IPO firms
+#' that issued stocks in the previous n months
+#'
+#' @param time_index_df
+#'
+#' @param ipo_dates_df
+#'
+make_time_series_ipo_list = function(time_index_df,
+                                     ipo_dates_df,
+                                     ipo_duration_threshold){
+
+  ipo_time_series_list_df = time_index_df %>%
+    crossing(ipo_dates_df) %>%
+    mutate(ipo_duration = (date - ipo_date) * 12) %>%
+    filter(ipo_duration >=0 & ipo_duration <= ipo_duration_threshold) %>%
+    select(-c("ipo_duration", "ipo_date"))
+
+
+  return(ipo_time_series_list_df)
+
+}
+
+
+
 #' This function makes price df by merging price data for securities and
 #' benchmarks
 #'

### 2023-06-05 R/robustness_auxilary_functions.R
add car and bhar export

@@ -71,7 +71,7 @@ convert_to_trading_months = function(price_df){
     group_by(id, id_control) %>%
     mutate(date = as.numeric(date - min(date))) %>%
     filter(!date == 0) %>%
-    mutate(date = (date %/% 22) + 1) %>%
+    mutate(date = (date %/% 21) + 1) %>%
     ungroup()
 
   monthly_df = monthly_df %>%

### 2023-06-21 R/robustness_auxilary_functions.R
update t stat functions

@@ -97,9 +97,9 @@ t_skew_adjusted = function(ar_vec, n_comps){
 
   S = mean_ar / sd_ar
 
-  gamma_hat = (sum(ar_vec - mean_ar) ^ 3) / (n_comps * sd_ar ^ 3)
+  gamma_hat = sum((ar_vec - mean_ar) ^ 3) / (n_comps * sd_ar ^ 3)
 
-  t_sa = sqrt(n_comps) * (S + (gamma_hat * S) / 3 + gamma_hat / (6 * n_comps))
+  t_sa = sqrt(n_comps) * (S + (gamma_hat * S^2) / 3 + gamma_hat / (6 * n_comps))
 
   return(t_sa)
 
@@ -109,13 +109,15 @@ t_skew_adjusted = function(ar_vec, n_comps){
 
 #' This function calculates t statistic
 #'
-t_stat = function(ar_vec, n_comps){
+t_statistic = function(ar_vec, n_comps){
 
 mean_ar = mean(ar_vec)
 
 sd_ar = sd(ar_vec)
 
-t_stat = mean_ar / (sd_ar / sqrt(n_comps))
+se = sd_ar / sqrt(n_comps)
+
+t_stat = mean_ar / se
 
 return(t_stat)
 

### 2023-06-22 R/robustness_auxilary_functions.R
update car calculation

@@ -3,7 +3,8 @@
 #' price df (matched ipo and control)
 #'
 #'
-#'
+#' @return a buy-and-hold return for each ipo firm and each of the
+#'  control group firms for this ipo firm for three horizons
 
 calculate_bhar_from_price_df = function(price_df,
                                         target_duration,
@@ -17,13 +18,15 @@ calculate_bhar_from_price_df = function(price_df,
     slice(1, length(duration)) %>%
     summarise(bhar_ipo = (price_ipo[2] / price_ipo[1]) - 1,
               bhar_control = (price_control[2] / price_control[1]) - 1,
-              bhar_abnormal = bhar_ipo - bhar_control,
               duration = duration[2], .groups = "drop")
 
   bhar_df = bhar_df %>%
     mutate(dur_diff = target_duration / duration - 1) %>%
     filter(dur_diff <= duration_tolerance) %>%
-    select(-duration, -dur_diff)
+    select(-duration, -dur_diff) %>%
+    group_by(id) %>%
+    summarise(across(contains("bhar"), mean), .groups = "drop") %>%
+    mutate(bhar_abnormal = bhar_ipo - bhar_control)
 
 
   return(bhar_df)
@@ -31,6 +34,60 @@ calculate_bhar_from_price_df = function(price_df,
 
 
 }
+
+#' This function calculates abnormal returns from
+#' price df (matched ipo and control)
+#'
+#'
+#' @return an abnormal return for each ipo firm and each of the
+#'  control group firms for this ipo firm for three horizons
+
+calculate_car_from_price_df = function(price_df,
+                                        target_duration,
+                                        duration_tolerance = 0.05){
+
+  price_df = price_df %>%
+    group_by(id, id_control) %>%
+    mutate(duration = as.numeric(date - min(date))) %>%
+    ungroup() %>%
+    filter(duration < target_duration)
+
+
+  valid_duration_secs = price_df %>%
+    group_by(id, id_control) %>%
+    summarise(max_duration = max(duration), .groups = "drop") %>%
+    filter(target_duration / max_duration - 1 <= duration_tolerance) %>%
+    select(id, id_control)
+
+
+  ret_df = price_df %>%
+    inner_join(valid_duration_secs, by = c("id", "id_control")) %>%
+    group_by(id, id_control) %>%
+    arrange(date) %>%
[…]

### 2023-07-26 R/robustness_auxilary_functions.R
add monthly car and function

@@ -42,46 +42,31 @@ calculate_bhar_from_price_df = function(price_df,
 #' @return an abnormal return for each ipo firm and each of the
 #'  control group firms for this ipo firm for three horizons
 
-calculate_car_from_price_df = function(price_df,
-                                        target_duration,
-                                        duration_tolerance = 0.05){
-
-  price_df = price_df %>%
-    group_by(id, id_control) %>%
-    mutate(duration = as.numeric(date - min(date))) %>%
-    ungroup() %>%
-    filter(duration < target_duration)
-
-
-  valid_duration_secs = price_df %>%
-    group_by(id, id_control) %>%
-    summarise(max_duration = max(duration), .groups = "drop") %>%
-    filter(target_duration / max_duration - 1 <= duration_tolerance) %>%
-    select(id, id_control)
+calculate_car_from_price_df = function(price_df){
 
 
   ret_df = price_df %>%
-    inner_join(valid_duration_secs, by = c("id", "id_control")) %>%
     group_by(id, id_control) %>%
     arrange(date) %>%
-    mutate(across(c("price_ipo","price_control"), ~./dplyr::lag(.) - 1)) %>%
+    mutate(across(c("price_ipo", "price_control"),
+                  ~ . / dplyr::lag(.,1) - 1)) %>%
     ungroup() %>%
+    filter(complete.cases(.)) %>%
     rename_with(~str_replace_all(.,"price","ret")) %>%
-    filter(complete.cases(.))
-
-
-  ar_df = ret_df %>%
-    group_by(id, duration) %>%
-    summarise(across(contains("ret"), mean), .groups = "drop") %>%
     mutate(ret_abnormal = ret_ipo - ret_control)
 
-  car_df = ar_df %>%
-    group_by(id) %>%
-    summarise(car_abnormal = sum(ret_abnormal), .groups = "drop")
+  cumret_df = ret_df %>%
+    group_by(id, id_control) %>%
+    arrange(date) %>%
+    mutate(across(contains("ret"),cumsum)) %>%
+    ungroup() %>%
+    rename_with(~str_replace_all(.,"ret","cum_ret"))
 
+  cumret_df = cumret_df %>%
+    group_by(date, id) %>%
+    summarise(across(contains("cum_ret"),mean), .groups = "drop")
 
-  return(car_df)
-
+  return(cumret_df)
 
 
 }
